New insights into the Weddell Sea ecosystem applying a network approach

### 2022-11-15 Manuscript/Manuscript.Rmd
Starting w/ Abstract

As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species. On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers. The following are arguments to have selected the unweighted properties. The degree has often been equated with importance to the structure and functioning of a community, i.e. perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a]. The trophic level offers information about how important a species is to its biotic community, i.e. top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a]. The trophic similarity measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].

>>>>

As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species. On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers. The following are arguments to have selected the unweighted properties. The degree has often been equated with importance to the structure and functioning of a community, i.e. perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a]. The trophic level offers information about how important a species is to its biotic community, i.e. top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a]. The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].

### 2022-11-15 Manuscript/Manuscript.tex
Starting w/ Abstract

As the weighted property we took into account the total mean interaction
strength, meaning the average strength of all species' interactions for
each species. On the other hand, we considered the following unweighted
properties: a) degree or the total number of trophic interactions,
summing up in- and out-coming interactions (role as predator and prey,
respectively); b) trophic level or the position in the food web relative
to primary producers/detritus; and c) trophic similarity or the trophic
overlap based on shared and unique resources and consumers. The
following are arguments to have selected the unweighted properties. The
degree has often been equated with importance to the structure and
functioning of a community, i.e.~perturbations to high-degree species
may therefore have larger effects on the food web than perturbations to
low-degree species \citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e.~top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. The trophic
similarity measures one of the most important aspects of species'
niches, the trophic niche, and functional aspects of biodiversity
\citep{Martinez1991, Williams2000}.

>>>>

As the weighted property we took into account the total mean interaction
strength, meaning the average strength of all species' interactions for
each species. On the other hand, we considered the following unweighted
properties: a) degree or the total number of trophic interactions,
summing up in- and out-coming interactions (role as predator and prey,
respectively); b) trophic level or the position in the food web relative
to primary producers/detritus; and c) trophic similarity or the trophic
overlap based on shared and unique resources and consumers. The
following are arguments to have selected the unweighted properties. The
degree has often been equated with importance to the structure and
functioning of a community, i.e.~perturbations to high-degree species
may therefore have larger effects on the food web than perturbations to
low-degree species \citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e.~top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. The trophic
similarity is an index of trophic overlap considering the set of prey
and predators for a pair of species; it measures one of the most
important aspects of species' niches, the trophic niche, and functional
aspects of biodiversity \citep{Martinez1991, Williams2000}.
